MINOS Handover Plots

### 2023-11-23 minos/validation/handovers.Rmd
Added dependency to household upscaling, and some WIP stuff on the msm model for chron_disease

```{r}
raw.nut <- raw.dat %>%
  select(pidp, age, time, nutrition_quality)
base.nut <- base.dat %>%
  select(pidp, age, time, nutrition_quality)

spaghetti_plot(nut.spag, 'nutrition_quality',
               save = shall.we.save,
               save.path = save.path)

density_ridges(nut.spag, "nutrition_quality",
               save = T,
               save.path = save.path)

@@

```{r}
handover_ordinal(raw.dat, base.dat, var = 'auditc', save = shall.we.save)
```

@@

```{r}
handover_ordinal(raw.dat, base.dat, var = 'active', save = shall.we.save)
```

@@

```{r}
#handover_boxplots(raw.dat, base.dat, 'matdep')
#handover_lineplots(raw.dat, base.dat, 'matdep')
handover_ordinal(raw.dat, base.dat, var = 'matdep', save = shall.we.save)
```

>>>>

```{r}
# raw.nut <- raw.dat %>%
#   select(pidp, age, time, nutrition_quality)
# base.nut <- base.dat %>%
#   select(pidp, age, time, nutrition_quality)
# 
# nut.spag <- rbind(raw.nut, base.nut)
# 
# spaghetti_plot(nut.spag, 'nutrition_quality',
#                save = shall.we.save,
#                save.path = save.path)
# 
# 
# density_ridges(nut.spag, "nutrition_quality",
#                save = T,
#                save.path = save.path)
# 
# rm(raw.nut, base.nut, nut.spag)
```

@@

```{r}
handover_ordinal(raw.dat, base.dat, var = 'auditc', save = shall.we.save)

raw.2020.alc <- raw.dat %>% 
  filter(time == 2020) %>%
  group_by(auditc) %>%
  summarise(n = n()) %>%
  mutate(prop = n / sum(n))

```

@@

```{r}
handover_ordinal(raw.dat, base.dat, var = 'active', save = shall.we.save)

raw.2020.phys <- raw.dat %>% 
  filter(time == 2020) %>%
  group_by(active) %>%
  summarise(n = n()) %>%
  mutate(prop = n / sum(n))
```

@@

```{r}
#handover_boxplots(raw.dat, base.dat, 'matdep')
#handover_lineplots(raw.dat, base.dat, 'matdep')
handover_ordinal(raw.dat, base.dat, var = 'matdep', save = shall.we.save)

raw.dat$chron_disease <- as.factor(raw.dat$chron_disease)
raw.2020.cd <- raw.dat %>%
  select(time, chron_disease, age) %>%
  filter(time == 2020) %>%
  mutate(age_group = cut(age, 
                         breaks = c(0,20,30,40,50,60,70,80,90,100,120),
                         labels = c('16-19', '20-30', '30-40', '40-50', '50-60', '60-70', '70-80', '80-90', '90-100', '100+'))) %>%
  group_by(age_group, chron_disease) %>%
  summarise(n = n()) %>%
  group_by(age_group) %>%
  mutate(prop = n / sum(n),
         perc = prop * 100)
  # mutate(prop = n() / sum(n),
  #        perc = prop * 100)

raw.2020.cd

ggplot(raw.2020.cd, aes(x = age_group, y = perc, group = chron_disease, colour = chron_disease, fill = chron_disease)) +
  geom_col(position = 'dodge') +
  xlab('Age Group') +
  ylab('Proportion')
```
